### 2022-12-09 SALT-abstract/SALT-abstract.tex
updates

\usepackage{setspace}
\begin{document}

\bibliographystyle{plainnat}
% \enablehyphenation
% \vspace{-2em}
% \maketitle
\textcolor{white}{.} \vspace{-3.9\baselineskip} \\
\begin{center}
	\textbf{\large%\thetitle
		%A diverse family (of sentences)\\ 
		Projection differs across embedding operators---but not like you think}
\end{center}

\vspace*{-.4cm}

\noindent 
We present experimental evidence that i) the projection of the content of the clausal complement of attitude predicates varies across entailment-canceling operators (negation, question, modal, conditional) and ii) this by-operator variation differs across attitude predicates. Our results do not align with the long-standing distinction between factive and semi-factive predicates (see, e.g., \citealt{karttunen_observations_1971,djarv_cognitive_2018}). Instead, the observed by-operator variation groups predicates by lexical semantic/pragmatic properties that raise important questions for future research on projection.

\noindent
{\bf Projection across entailment-cancelling operators.} Interpreters may infer that a speaker who utters one of the attitude ascriptions in  \ref{ex:family} is committed to the truth of the content of the complement (CC), that Julian dances salsa, even though the complement occurs under an entailment-canceling operator, such as negation \ref{ex:neg}, a polar question \ref{ex:q}, a modal \ref{ex:mod}, or a conditional \ref{ex:cond}.

@@

\noindent
{\bf Results.} Fig.~\ref{fig:figure1} plots the mean projection ratings for the 20 attitude predicates by embedding operator; the predicates are ordered by their mean projection across all operators (\emph{be annoyed} has the highest overall projection mean). We observe by-operator variation in projection means as well as differences across the predicates in by-operator variation: For instance, whereas the CC of \emph{be annoyed} projects more from under questions and negation than from under conditionals and modals, the CC of \emph{know} projects more from under questions than from under conditionals and negation, and the CC of \emph{discover} projects more from under questions and conditionals than from under negation and modals. These results are not aligned with the distinction between factive and semi-factive predicates proposed in \citealt{karttunen_observations_1971} or assumed in \citealt{djarv_cognitive_2018}: Contrary to assumption, the CC of the purportedly factive predicate \emph{be annoyed} does not project invariably from all four operators, and the CC of the purportedly semi-factive predicate \emph{discover} does not project more from under negation than the other three operators. For {\em know}, we observe a third pattern -- one that is not aligned with a classification as a factive nor as a semi-factive predicate.

==== THIS IS AS FAR AS I've COME ====

@@

\noindent
{\bf Discussion.}

We observe that projection varies by predicate (e.g., the CC of \emph{be annoyed} is more projective than that of \emph{discover}; replicating the results of  \citealt{degen-tonhauser-language}).

No categorical distinction between factive and non-factive predicates either

add discussion about verb classes here

@@

\begin{figure}[t]
		\vspace{-.8\baselineskip}
		\centering
		\includegraphics[width=\textwidth]{graphs/proj-by-both.pdf}\vspace{-1.2\baselineskip}
		\caption{\small Mean certainty ratings by predicate and operator with 95\% bootstrapped confidence intervals. Embedding operator coded by letter and color:  \texttt{N} (blue): negation, \texttt{M} (green): modals, \texttt{C} (red): conditional antecedents, \texttt{Q} (purple): polar questions.}
		\label{fig:figure1}
	\end{figure}

@@

>>>>

\usepackage{setspace}

\parindent=2ex

\begin{document}

\bibliographystyle{plainnat}
% \enablehyphenation
% \vspace{-2em}
% \maketitle

\begin{center}
	\textbf{\large%\thetitle
		%A diverse family (of sentences)\\ 
		Projection differs across embedding operators---but not like you think}
\end{center}

\vspace*{-.6\baselineskip}
\noindent 
	We present experimental evidence that i) the projection of the content of the clausal complement of attitude predicates varies across entailment-canceling operators (negation, question, modal, conditional) and ii) this by-operator variation differs across attitude predicates. Our results do not align with the long-standing distinction between factive and semi-factive predicates (see, e.g., \citealp{karttunen_observations_1971,hooper_applicability_1973,djarv_cognitive_2018}, though see \citealp{beaver_have_2010}). Instead, the observed by-operator variation groups predicates by lexical semantic/pragmatic properties that raise important questions for future research on projection.

\noindent
	{\bf Projection across entailment-cancelling operators.} Interpreters may infer that a speaker who utters one of the attitude ascriptions in  \ref{ex:family} is committed to the truth of the content of the complement (CC),
	% that Julian dances salsa,
	even though it occurs under an entailment-canceling operator, such as negation \ref{ex:neg}, a polar question \ref{ex:q}, a modal \ref{ex:mod}, or a conditional \ref{ex:cond}.

@@

\noindent
{\bf Results.}
	Fig.~\ref{fig:figure1} shows the mean projection ratings for the 20 attitude predicates by embedding operator; the predicates are ordered by their mean projection across all operators (\emph{be annoyed} has the highest overall projection mean). We observe by-operator variation in projection means as well as differences across the predicates in by-operator variation: For instance, whereas the CC of \emph{be annoyed} projects more from under negation (and questions) than from under conditionals and modals, the CC of \emph{know} projects less from under negation than under questions, but more from under negation than from under modals, and the CC of \emph{discover} projects less from negation than from under conditionals and questions, and more from under negation than modals. These results (which are supported by linear mixed effects models, see Table \ref{t:models}) are not aligned with the distinction between factive and semi-factive predicates proposed in \citealt{karttunen_observations_1971} or assumed in \citealt{djarv_cognitive_2018}: Contrary to assumption, the CC of the purportedly factive predicate \emph{be annoyed} does not project invariably from all four operators, and the CC of the purportedly semi-factive predicate \emph{discover} does not project more from under negation than the other three operators. For {\em know}, we observe a third pattern -- one that is not aligned with a classification as a factive nor as a semi-factive predicate.

@@

\noindent
{\bf Discussion and Conclusion.} 
	Our results clearly show that different entailment-cancelling operators affect projection in different ways, and that the effect of entailment-cancelling operator on projection differs for different verbs. The picture that emerges could not be characterized in terms of Karttunen's characterization of (semi)factives. Our results indicate a need for a more nuanced view of the family-of-sentences diagnostics of projection, as well as a better understanding of the effect of the interaction between lexical semantics and operators on projection.

	Further, we were able to replicate the results of \citealp{degen_are_2022}), observing that projection varies by predicate (e.g., the CC of \emph{be annoyed} is more projective than that of \emph{discover}, and finding no categorical distinction between factive and non-factive predicates either.

	In spite of a lack of categorical distinctions about the projection behavior of our verbs, we can find some interesting patterns. \textbf{Figure \ref{fig:figure2}} gives the mean certainty ratings for the four operators by verb, for some groups of our verbs that group together in the way that they show by-operator variation. We highlight four \lq projection-profiles\rq here: the verbs \emph{pretend, think} are the only verbs that are most projective under negation compared to all other operators (\texttt{N} $>$ \texttt{M, Q, C}). \emph{annouce, confess, admit,} and \emph{reveal} are most projective under conditionals, while there is also a tendency that there is more projection from questions compared to modals and negation, a difference that may not be robust for \emph{announce} (\texttt{C} $>$ \texttt{Q} \textcolor{gray!40}{$>_?$} \texttt{M, N}). \emph{prove, confirm,} and \emph{establish} are more projective under modals and conditionals than under questions and negation (\texttt{M, C} $>$ \texttt{Q, N}). Finally, \emph{inform} and \emph{know} are most projective under questions, and least projective under modals (\texttt{Q} $>$ \texttt{N, Q} $>$ \texttt{M}).

	The picture that emerges is complex and requires a nuanced view of lexical effects on projection. I raises the question of how lexical differences between verbs could explain why certain verbs project more from under certain operators and less from others. While much previous work on this question has based their generalizations on impressionistic judgments, empirically establishing different projection-profiles associated with verbs therefore provides a basis for future research on lexical effects on projection.

@@

\begin{figure}[h]
	% \vspace{-\baselineskip}
	\centering
	\scalebox{.9}{\includegraphics[width=\textwidth]{graphs/proj-by-both.pdf}}\vspace{-1.7\baselineskip}
	\caption{\small Mean certainty ratings by predicate and operator with 95\% bootstrapped confidence intervals. Embedding operator coded by letter and color:  \texttt{N} (blue): negation, \texttt{M} (green): modals, \texttt{C} (red): conditional antecedents, \texttt{Q} (purple): polar questions.}
	\label{fig:figure1}
\end{figure}

\begin{table}[h]
	\centering
	\vspace{-.7\baselineskip}
	\scalebox{.85}{
		\begin{tabular}{llrrrr}
			Model & & Estimate & Std. Error & t-value\\
			\midrule
			\#1 & Intercept: \emph{be annoyed}/negation & 0.87 & 0.01  & 75.8 & *** \\
			& operator: conditional & -0.12 & 0.02  & -7.38 & *** \\
			& operator: modal & -0.16 & 0.02  & -10.04 & *** \\
			& operator: question & 0.02 & 0.01  & 1.74 & n.s. \\
			\midrule
			\#2 & Intercept: \emph{know}/negation & 0.79 & 0.01 &  69.24 & *** \\
			&		operator: conditional & -0.001 & 0.02  & -0.08 & n.s. \\
			&		operator: modal  & -0.14 & 0.02  & -9.2 & *** \\
			&		operator: question & 0.08 & 0.01  & 5.72 & *** \\
			\midrule
			\#3 & Intercept: \emph{discover}/negation & 0.68 & 0.01  & 59.48 & *** \\
			& operator: conditional & 0.11 & 0.02  & 7.11 & *** \\
			&		operator: modal & -0.06 & 0.02  & -3.6 & *** \\
			&		operator: question & 0.1 & 0.01  & 7.07 & *** \\

			\bottomrule
		\end{tabular}
	}
	\vspace{-.3\baselineskip}
	\caption{\small Relevant parts of three linear mixed effects models that predict certainty ratings from a fixed effect of operator, predicate, and their interaction, with random effects for participant and CC. Models were fit with \texttt{lme4, lmertest} in \texttt{R}; \citealp{bates_fitting_2015,kuznetsova_lmertest_2016,r_core_team_r_2014}.}\label{t:models}
\end{table}

\begin{figure}[h]
	\hspace{-2em}
	\begin{minipage}{1.1\textwidth}\centering
		\includegraphics[width=.24\linewidth]{graphs/profile1.pdf}
		\includegraphics[width=.24\linewidth]{graphs/profile2.pdf}
		% \includegraphics[width=.32\linewidth]{graphs/profile3.pdf}\\
		\includegraphics[width=.24\linewidth]{graphs/profile4.pdf}
		\includegraphics[width=.24\linewidth]{graphs/profile5.pdf}
	\end{minipage}
	\vspace{-\baselineskip}
	\caption{Mean certainty-ratings by operator for each verb, showing different \lq verb-profiles\rq.}
	\label{fig:figure2}
\end{figure}

@@

% \begin{table}[ht]
% 	\caption{Model output w \texttt{be\_annoyed/n} as baseline}
% 	\label{tab:annoyed-n}
% 	\centering

% 	\begin{tabular}{lrrrrr}
% 		\toprule
% 		  & Estimate & Std. Error & df & t value & Pr(>|t|)\\
% 		\midrule
% 		(Intercept) & 0.8669958 & 0.0114402 & 1479.204 & 75.7850523 & 0.0000000\\
% 		opc & -0.1155850 & 0.0156641 & 26227.368 & -7.3789836 & 0.0000000\\
% 		opm & -0.1564480 & 0.0155858 & 26288.139 & -10.0378702 & 0.0000000\\
% 		opq & 0.0249138 & 0.0143090 & 56826.915 & 1.7411232 & 0.0816674\\
% 		verbsuggest & -0.6162683 & 0.0134941 & 54372.895 & -45.6694112 & 0.0000000\\
% 		\addlinespace
% 		verbacknowledge & -0.2204417 & 0.0134948 & 54373.777 & -16.3352724 & 0.0000000\\
% 		verbadmit & -0.3402430 & 0.0134933 & 54371.874 & -25.2156750 & 0.0000000\\
% 		verbannounce & -0.3607504 & 0.0134931 & 54371.547 & -26.7359958 & 0.0000000\\
% 		verbbe\_right & -0.6638924 & 0.0134936 & 54372.293 & -49.2003974 & 0.0000000\\
% 		verbconfess & -0.3681695 & 0.0134949 & 54373.904 & -27.2820517 & 0.0000000\\
% 		\addlinespace
% 		verbconfirm & -0.6338363 & 0.0134931 & 54371.657 & -46.9746939 & 0.0000000\\
% 		verbdemonstrate & -0.5307026 & 0.0134935 & 54372.157 & -39.3301466 & 0.0000000\\
% 		verbdiscover & -0.1864716 & 0.0134942 & 54372.992 & -13.8186520 & 0.0000000\\
% 		verbestablish & -0.5542561 & 0.0134933 & 54371.853 & -41.0764079 & 0.0000000\\
% 		verbhear & -0.1956794 & 0.0134938 & 54372.473 & -14.5014554 & 0.0000000\\
% 		\addlinespace
% 		verbinform & -0.1374428 & 0.0134945 & 54373.345 & -10.1851106 & 0.0000000\\
% 		verbknow & -0.0748953 & 0.0134936 & 54372.288 & -5.5504197 & 0.0000000\\
% 		verbpretend & -0.5049533 & 0.0134944 & 54373.218 & -37.4195409 & 0.0000000\\
% 		verbprove & -0.6364950 & 0.0134935 & 54372.138 & -47.1704273 & 0.0000000\\
% 		verbreveal & -0.3057814 & 0.0134937 & 54372.418 & -22.6609884 & 0.0000000\\
% 		\addlinespace
% 		verbsay & -0.5419725 & 0.0134925 & 54370.770 & -40.1685159 & 0.0000000\\
% 		verbsee & -0.1827512 & 0.0134932 & 54371.791 & -13.5438968 & 0.0000000\\
% 		verbthink & -0.5101198 & 0.0134930 & 54371.491 & -37.8062103 & 0.0000000\\
% 		opc:verbsuggest & 0.1594325 & 0.0190634 & 54372.626 & 8.3632939 & 0.0000000\\
% 		opm:verbsuggest & 0.1766113 & 0.0189718 & 54372.046 & 9.3091498 & 0.0000000\\
% 		\addlinespace
% 		opq:verbsuggest & -0.0737648 & 0.0192906 & 54372.717 & -3.8238781 & 0.0001315\\
% 		opc:verbacknowledge & 0.1945569 & 0.0190630 & 54372.333 & 10.2059764 & 0.0000000\\
% 		opm:verbacknowledge & 0.1100553 & 0.0189729 & 54373.070 & 5.8006461 & 0.0000000\\
% 		opq:verbacknowledge & 0.0672935 & 0.0192909 & 54372.991 & 3.4883599 & 0.0004864\\
% 		opc:verbadmit & 0.2803349 & 0.0190626 & 54371.933 & 14.7060204 & 0.0000000\\
% 		\addlinespace
% 		opm:verbadmit & 0.1810708 & 0.0189717 & 54371.994 & 9.5442376 & 0.0000000\\
% 		opq:verbadmit & 0.0440050 & 0.0192896 & 54371.832 & 2.2812856 & 0.0225354\\
% 		opc:verbannounce & 0.2503929 & 0.0190639 & 54373.132 & 13.1343759 & 0.0000000\\
% 		opm:verbannounce & 0.1633026 & 0.0189721 & 54372.338 & 8.6075049 & 0.0000000\\
% 		opq:verbannounce & 0.0017532 & 0.0192899 & 54372.121 & 0.0908892 & 0.9275810\\
% 		\addlinespace
% 		opc:verbbe\_right & 0.1424317 & 0.0190623 & 54371.698 & 7.4718895 & 0.0000000\\
% 		opm:verbbe\_right & 0.2582399 & 0.0189717 & 54371.967 & 13.6118412 & 0.0000000\\
% 		opq:verbbe\_right & -0.0776846 & 0.0192897 & 54371.974 & -4.0272512 & 0.0000565\\
% 		opc:verbconfess & 0.3111230 & 0.0190643 & 54373.455 & 16.3196605 & 0.0000000\\
% 		opm:verbconfess & 0.1837114 & 0.0189741 & 54374.125 & 9.6821973 & 0.0000000\\
% 		\addlinespace
% 		opq:verbconfess & 0.0393640 & 0.0192890 & 54371.320 & 2.0407459 & 0.0412809\\
% 		opc:verbconfirm & 0.2963833 & 0.0190629 & 54372.237 & 15.5476205 & 0.0000000\\
% 		opm:verbconfirm & 0.3663333 & 0.0189721 & 54372.324 & 19.3090505 & 0.0000000\\
% 		opq:verbconfirm & 0.0312870 & 0.0192902 & 54372.377 & 1.6219108 & 0.1048282\\
% 		opc:verbdemonstrate & 0.2854366 & 0.0190647 & 54373.829 & 14.9719656 & 0.0000000\\
% 		\addlinespace
% 		opm:verbdemonstrate & 0.2783816 & 0.0189716 & 54371.830 & 14.6736292 & 0.0000000\\
% 		opq:verbdemonstrate & 0.0753554 & 0.0192892 & 54371.520 & 3.9066023 & 0.0000937\\
% 		opc:verbdiscover & 0.2270099 & 0.0190632 & 54372.450 & 11.9082962 & 0.0000000\\
% 		opm:verbdiscover & 0.1002424 & 0.0189726 & 54372.795 & 5.2835252 & 0.0000001\\
% 		opq:verbdiscover & 0.0762282 & 0.0192898 & 54372.014 & 3.9517423 & 0.0000777\\
% 		\addlinespace
% 		opc:verbestablish & 0.2570817 & 0.0190633 & 54372.539 & 13.4857080 & 0.0000000\\
% 		opm:verbestablish & 0.2879581 & 0.0189714 & 54371.677 & 15.1785426 & 0.0000000\\
% 		opq:verbestablish & 0.0061604 & 0.0192893 & 54371.583 & 0.3193687 & 0.7494481\\
% 		opc:verbhear & 0.2016309 & 0.0190630 & 54372.273 & 10.5770983 & 0.0000000\\
% 		opm:verbhear & -0.0046313 & 0.0189714 & 54371.681 & -0.2441216 & 0.8071376\\
% 		\addlinespace
% 		opq:verbhear & 0.0756021 & 0.0192902 & 54372.373 & 3.9192008 & 0.0000890\\
% 		opc:verbinform & 0.1278740 & 0.0190645 & 54373.631 & 6.7074362 & 0.0000000\\
% 		opm:verbinform & 0.0141486 & 0.0189741 & 54374.122 & 0.7456761 & 0.4558664\\
% 		opq:verbinform & 0.0587564 & 0.0192913 & 54373.322 & 3.0457537 & 0.0023221\\
% 		opc:verbknow & 0.1142699 & 0.0190629 & 54372.206 & 5.9943629 & 0.0000000\\
% 		\addlinespace
% 		opm:verbknow & 0.0130032 & 0.0189709 & 54371.181 & 0.6854301 & 0.4930755\\
% 		opq:verbknow & 0.0569598 & 0.0192897 & 54371.975 & 2.9528579 & 0.0031498\\
% 		opc:verbpretend & -0.0902047 & 0.0190640 & 54373.155 & -4.7316842 & 0.0000022\\
% 		opm:verbpretend & -0.0194245 & 0.0189738 & 54373.822 & -1.0237558 & 0.3059552\\
% 		opq:verbpretend & -0.2196823 & 0.0192900 & 54372.250 & -11.3883795 & 0.0000000\\
% 		\addlinespace
% 		opc:verbprove & 0.2579585 & 0.0190627 & 54372.031 & 13.5320999 & 0.0000000\\
% 		opm:verbprove & 0.3580525 & 0.0189720 & 54372.223 & 18.8726898 & 0.0000000\\
% 		opq:verbprove & 0.0230805 & 0.0192908 & 54372.899 & 1.1964509 & 0.2315259\\
% 		opc:verbreveal & 0.2902650 & 0.0190644 & 54373.511 & 15.2255216 & 0.0000000\\
% 		opm:verbreveal & 0.1767476 & 0.0189723 & 54372.513 & 9.3160804 & 0.0000000\\
% 		\addlinespace
% 		opq:verbreveal & 0.0665887 & 0.0192906 & 54372.717 & 3.4518763 & 0.0005571\\
% 		opc:verbsay & 0.1985351 & 0.0190618 & 54371.193 & 10.4153412 & 0.0000000\\
% 		opm:verbsay & 0.1451974 & 0.0189723 & 54372.495 & 7.6531273 & 0.0000000\\
% 		opq:verbsay & -0.1815738 & 0.0192889 & 54371.195 & -9.4133926 & 0.0000000\\
% 		opc:verbsee & 0.2175191 & 0.0190629 & 54372.234 & 11.4105822 & 0.0000000\\
% 		\addlinespace
% 		opm:verbsee & 0.0594092 & 0.0189723 & 54372.499 & 3.1313655 & 0.0017409\\
% 		opq:verbsee & 0.1108274 & 0.0192896 & 54371.840 & 5.7454526 & 0.0000000\\
% 		opc:verbthink & 0.0023197 & 0.0190619 & 54371.272 & 0.1216913 & 0.9031440\\
% 		opm:verbthink & 0.0145577 & 0.0189717 & 54371.965 & 0.7673367 & 0.4428847\\
% 		opq:verbthink & -0.1738342 & 0.0192903 & 54372.438 & -9.0115053 & 0.0000000\\
% 		\bottomrule
% 	\end{tabular}
% \end{table}

% \newpage

% \begin{table}[ht]
% 	\caption{Model output w \texttt{discover/n} as baseline}
% 	\label{tab:discover-n}
% 	\centering

% 	\begin{tabular}{lrrrrr}
% 		\toprule
% 		  & Estimate & Std. Error & df & t value & Pr(>|t|)\\
% 		\midrule
% 		(Intercept) & 0.6805242 & 0.0114403 & 1479.217 & 59.4849565 & 0.0000000\\
% 		opc & 0.1114249 & 0.0156639 & 26226.686 & 7.1134644 & 0.0000000\\
% 		opm & -0.0562056 & 0.0155855 & 26286.826 & -3.6062779 & 0.0003112\\
% 		opq & 0.1011420 & 0.0143103 & 56828.295 & 7.0677830 & 0.0000000\\
% 		verbbe\_annoyed & 0.1864716 & 0.0134942 & 54372.998 & 13.8186521 & 0.0000000\\
% 		\addlinespace
% 		verbsuggest & -0.4297967 & 0.0134937 & 54372.361 & -31.8516905 & 0.0000000\\
% 		verbacknowledge & -0.0339702 & 0.0134936 & 54372.308 & -2.5174950 & 0.0118221\\
% 		verbadmit & -0.1537714 & 0.0134942 & 54372.985 & -11.3953857 & 0.0000000\\
% 		verbannounce & -0.1742788 & 0.0134947 & 54373.649 & -12.9145926 & 0.0000000\\
% 		verbbe\_right & -0.4774208 & 0.0134935 & 54372.079 & -35.3816304 & 0.0000000\\
% 		\addlinespace
% 		verbconfess & -0.1816980 & 0.0134936 & 54372.192 & -13.4655376 & 0.0000000\\
% 		verbconfirm & -0.4473648 & 0.0134944 & 54373.311 & -33.1517710 & 0.0000000\\
% 		verbdemonstrate & -0.3442310 & 0.0134928 & 54371.247 & -25.5121517 & 0.0000000\\
% 		verbestablish & -0.3677846 & 0.0134928 & 54371.167 & -27.2579106 & 0.0000000\\
% 		verbhear & -0.0092079 & 0.0134940 & 54372.798 & -0.6823676 & 0.4950095\\
% 		\addlinespace
% 		verbinform & 0.0490288 & 0.0134942 & 54373.066 & 3.6333114 & 0.0002801\\
% 		verbknow & 0.1115762 & 0.0134931 & 54371.668 & 8.2691029 & 0.0000000\\
% 		verbpretend & -0.3184818 & 0.0134943 & 54373.176 & -23.6011440 & 0.0000000\\
% 		verbprove & -0.4500234 & 0.0134934 & 54372.042 & -33.3512833 & 0.0000000\\
% 		verbreveal & -0.1193099 & 0.0134941 & 54372.880 & -8.8416323 & 0.0000000\\
% 		\addlinespace
% 		verbsay & -0.3555009 & 0.0134943 & 54373.168 & -26.3444678 & 0.0000000\\
% 		verbsee & 0.0037204 & 0.0134930 & 54371.450 & 0.2757288 & 0.7827574\\
% 		verbthink & -0.3236483 & 0.0134936 & 54372.197 & -23.9853913 & 0.0000000\\
% 		opc:verbbe\_annoyed & -0.2270099 & 0.0190632 & 54372.453 & -11.9082963 & 0.0000000\\
% 		opm:verbbe\_annoyed & -0.1002424 & 0.0189726 & 54372.798 & -5.2835253 & 0.0000001\\
% 		\addlinespace
% 		opq:verbbe\_annoyed & -0.0762282 & 0.0192898 & 54372.017 & -3.9517423 & 0.0000777\\
% 		opc:verbsuggest & -0.0675773 & 0.0190625 & 54371.851 & -3.5450396 & 0.0003929\\
% 		opm:verbsuggest & 0.0763690 & 0.0189709 & 54371.211 & 4.0255864 & 0.0000569\\
% 		opq:verbsuggest & -0.1499930 & 0.0192910 & 54373.069 & -7.7752981 & 0.0000000\\
% 		opc:verbacknowledge & -0.0324529 & 0.0190617 & 54371.116 & -1.7025196 & 0.0886637\\
% 		\addlinespace
% 		opm:verbacknowledge & 0.0098129 & 0.0189711 & 54371.417 & 0.5172570 & 0.6049789\\
% 		opq:verbacknowledge & -0.0089347 & 0.0192902 & 54372.396 & -0.4631724 & 0.6432426\\
% 		opc:verbadmit & 0.0533251 & 0.0190632 & 54372.508 & 2.7972739 & 0.0051554\\
% 		opm:verbadmit & 0.0808284 & 0.0189728 & 54372.916 & 4.2602367 & 0.0000205\\
% 		opq:verbadmit & -0.0322232 & 0.0192908 & 54372.883 & -1.6703960 & 0.0948468\\
% 		\addlinespace
% 		opc:verbannounce & 0.0233831 & 0.0190642 & 54373.367 & 1.2265427 & 0.2199998\\
% 		opm:verbannounce & 0.0630602 & 0.0189726 & 54372.754 & 3.3237576 & 0.0008887\\
% 		opq:verbannounce & -0.0744750 & 0.0192926 & 54374.465 & -3.8602856 & 0.0001134\\
% 		opc:verbbe\_right & -0.0845782 & 0.0190620 & 54371.360 & -4.4370099 & 0.0000091\\
% 		opm:verbbe\_right & 0.1579976 & 0.0189719 & 54372.163 & 8.3279685 & 0.0000000\\
% 		\addlinespace
% 		opq:verbbe\_right & -0.1539128 & 0.0192901 & 54372.283 & -7.9788617 & 0.0000000\\
% 		opc:verbconfess & 0.0841131 & 0.0190632 & 54372.437 & 4.4123417 & 0.0000102\\
% 		opm:verbconfess & 0.0834691 & 0.0189719 & 54372.142 & 4.3996174 & 0.0000109\\
% 		opq:verbconfess & -0.0368642 & 0.0192905 & 54372.632 & -1.9110088 & 0.0560087\\
% 		opc:verbconfirm & 0.0693734 & 0.0190644 & 54373.529 & 3.6388992 & 0.0002741\\
% 		\addlinespace
% 		opm:verbconfirm & 0.2660910 & 0.0189728 & 54372.917 & 14.0248948 & 0.0000000\\
% 		opq:verbconfirm & -0.0449413 & 0.0192914 & 54373.472 & -2.3295974 & 0.0198311\\
% 		opc:verbdemonstrate & 0.0584268 & 0.0190633 & 54372.586 & 3.0648793 & 0.0021786\\
% 		opm:verbdemonstrate & 0.1781393 & 0.0189714 & 54371.707 & 9.3898743 & 0.0000000\\
% 		opq:verbdemonstrate & -0.0008729 & 0.0192906 & 54372.707 & -0.0452486 & 0.9639093\\
% 		\addlinespace
% 		opc:verbestablish & 0.0300718 & 0.0190618 & 54371.161 & 1.5775980 & 0.1146638\\
% 		opm:verbestablish & 0.1877158 & 0.0189720 & 54372.212 & 9.8943713 & 0.0000000\\
% 		opq:verbestablish & -0.0700678 & 0.0192899 & 54372.103 & -3.6323635 & 0.0002811\\
% 		opc:verbhear & -0.0253789 & 0.0190637 & 54372.970 & -1.3312665 & 0.1831069\\
% 		opm:verbhear & -0.1048737 & 0.0189721 & 54372.368 & -5.5277707 & 0.0000000\\
% 		\addlinespace
% 		opq:verbhear & -0.0006261 & 0.0192909 & 54372.991 & -0.0324581 & 0.9741069\\
% 		opc:verbinform & -0.0991359 & 0.0190633 & 54372.605 & -5.2003420 & 0.0000002\\
% 		opm:verbinform & -0.0860938 & 0.0189733 & 54373.368 & -4.5376355 & 0.0000057\\
% 		opq:verbinform & -0.0174718 & 0.0192931 & 54374.843 & -0.9055994 & 0.3651520\\
% 		opc:verbknow & -0.1127399 & 0.0190628 & 54372.127 & -5.9141311 & 0.0000000\\
% 		\addlinespace
% 		opm:verbknow & -0.0872392 & 0.0189719 & 54372.149 & -4.5983336 & 0.0000043\\
% 		opq:verbknow & -0.0192684 & 0.0192895 & 54371.814 & -0.9989027 & 0.3178463\\
% 		opc:verbpretend & -0.3172145 & 0.0190639 & 54373.134 & -16.6395086 & 0.0000000\\
% 		opm:verbpretend & -0.1196669 & 0.0189725 & 54372.658 & -6.3073967 & 0.0000000\\
% 		opq:verbpretend & -0.2959105 & 0.0192916 & 54373.627 & -15.3388172 & 0.0000000\\
% 		\addlinespace
% 		opc:verbprove & 0.0309486 & 0.0190626 & 54371.908 & 1.6235265 & 0.1044827\\
% 		opm:verbprove & 0.2578102 & 0.0189728 & 54372.987 & 13.5883819 & 0.0000000\\
% 		opq:verbprove & -0.0531478 & 0.0192907 & 54372.839 & -2.7550974 & 0.0058694\\
% 		opc:verbreveal & 0.0632551 & 0.0190641 & 54373.234 & 3.3180321 & 0.0009071\\
% 		opm:verbreveal & 0.0765052 & 0.0189711 & 54371.383 & 4.0327309 & 0.0000552\\
% 		\addlinespace
% 		opq:verbreveal & -0.0096396 & 0.0192917 & 54373.669 & -0.4996755 & 0.6173056\\
% 		opc:verbsay & -0.0284748 & 0.0190633 & 54372.590 & -1.4936938 & 0.1352615\\
% 		opm:verbsay & 0.0449550 & 0.0189713 & 54371.586 & 2.3696339 & 0.0178092\\
% 		opq:verbsay & -0.2578020 & 0.0192911 & 54373.227 & -13.3637456 & 0.0000000\\
% 		opc:verbsee & -0.0094907 & 0.0190633 & 54372.613 & -0.4978528 & 0.6185898\\
% 		\addlinespace
% 		opm:verbsee & -0.0408332 & 0.0189714 & 54371.728 & -2.1523480 & 0.0313743\\
% 		opq:verbsee & 0.0345992 & 0.0192916 & 54373.623 & 1.7934827 & 0.0729013\\
% 		opc:verbthink & -0.2246902 & 0.0190628 & 54372.159 & -11.7868151 & 0.0000000\\
% 		opm:verbthink & -0.0856847 & 0.0189719 & 54372.175 & -4.5163904 & 0.0000063\\
% 		opq:verbthink & -0.2500624 & 0.0192911 & 54373.178 & -12.9625865 & 0.0000000\\
% 		\bottomrule
% 	\end{tabular}
% \end{table}

% \newpage

% \begin{table}[ht]
% 	\caption{Model output w \texttt{know/n} as baseline}
% 	\label{tab:discover-n}
% 	\centering

% 	\begin{tabular}{lrrrrr}
% 		\toprule
% 		  & Estimate & Std. Error & df & t value & Pr(>|t|)\\
% 		\midrule
% 		(Intercept) & 0.7921005 & 0.0114401 & 1479.182 & 69.2391632 & 0.0000000\\
% 		opc & -0.0013151 & 0.0156638 & 26226.099 & -0.0839558 & 0.9330922\\
% 		opm & -0.1434448 & 0.0155855 & 26286.727 & -9.2037503 & 0.0000000\\
% 		opq & 0.0818736 & 0.0143093 & 56827.205 & 5.7217106 & 0.0000000\\
% 		verbdiscover & -0.1115762 & 0.0134931 & 54371.661 & -8.2691029 & 0.0000000\\
% 		\addlinespace
% 		verbbe\_annoyed & 0.0748953 & 0.0134936 & 54372.286 & 5.5504198 & 0.0000000\\
% 		verbsuggest & -0.5413729 & 0.0134928 & 54371.215 & -40.1230775 & 0.0000000\\
% 		verbacknowledge & -0.1455464 & 0.0134940 & 54372.778 & -10.7859911 & 0.0000000\\
% 		verbadmit & -0.2653476 & 0.0134936 & 54372.243 & -19.6647018 & 0.0000000\\
% 		verbannounce & -0.2858550 & 0.0134935 & 54372.051 & -21.1847253 & 0.0000000\\
% 		\addlinespace
% 		verbbe\_right & -0.5889971 & 0.0134936 & 54372.234 & -43.6501264 & 0.0000000\\
% 		verbconfess & -0.2932742 & 0.0134933 & 54371.896 & -21.7347532 & 0.0000000\\
% 		verbconfirm & -0.5589410 & 0.0134943 & 54373.134 & -41.4204989 & 0.0000000\\
% 		verbdemonstrate & -0.4558072 & 0.0134931 & 54371.605 & -33.7807521 & 0.0000000\\
% 		verbestablish & -0.4793608 & 0.0134938 & 54372.501 & -35.5245129 & 0.0000000\\
% 		\addlinespace
% 		verbhear & -0.1207841 & 0.0134931 & 54371.608 & -8.9515418 & 0.0000000\\
% 		verbinform & -0.0625474 & 0.0134940 & 54372.811 & -4.6351853 & 0.0000036\\
% 		verbpretend & -0.4300580 & 0.0134939 & 54372.685 & -31.8704317 & 0.0000000\\
% 		verbprove & -0.5615997 & 0.0134934 & 54372.014 & -41.6202578 & 0.0000000\\
% 		verbreveal & -0.2308861 & 0.0134943 & 54373.179 & -17.1098402 & 0.0000000\\
% 		\addlinespace
% 		verbsay & -0.4670771 & 0.0134939 & 54372.578 & -34.6140392 & 0.0000000\\
% 		verbsee & -0.1078558 & 0.0134932 & 54371.715 & -7.9933523 & 0.0000000\\
% 		verbthink & -0.4352245 & 0.0134933 & 54371.896 & -32.2547883 & 0.0000000\\
% 		opc:verbdiscover & 0.1127399 & 0.0190628 & 54372.122 & 5.9141311 & 0.0000000\\
% 		opm:verbdiscover & 0.0872392 & 0.0189719 & 54372.145 & 4.5983336 & 0.0000043\\
% 		\addlinespace
% 		opq:verbdiscover & 0.0192684 & 0.0192895 & 54371.810 & 0.9989027 & 0.3178463\\
% 		opc:verbbe\_annoyed & -0.1142699 & 0.0190629 & 54372.206 & -5.9943630 & 0.0000000\\
% 		opm:verbbe\_annoyed & -0.0130032 & 0.0189709 & 54371.180 & -0.6854301 & 0.4930755\\
% 		opq:verbbe\_annoyed & -0.0569598 & 0.0192897 & 54371.974 & -2.9528580 & 0.0031498\\
% 		opc:verbsuggest & 0.0451626 & 0.0190614 & 54370.865 & 2.3693169 & 0.0178244\\
% 		\addlinespace
% 		opm:verbsuggest & 0.1636081 & 0.0189713 & 54371.561 & 8.6239932 & 0.0000000\\
